MADA Data Analysis Project

### 2021-11-13 code/analysis_code/03-P2.Data.rmd
Fixed manuscript and processing scripts
removing unfinished chunks

```{r}
p2mysummary <- summary(P2)
```

```{r}
#re-shape of a data frame (for easier saving/showing in manuscript)
P2summary_df <- data.frame(do.call(cbind, lapply(P2, summary)))
```
```{r}

```

@@

@@

```
######################################
#Data fitting/statistical analysis
######################################
```{r}
# fit glm.
# Ct~X= odds of Ct as response variable
P2.glm.fit<-glm(Ct~Dilution+Detector, data=P2P1)
#look at fit
print(tidy(P2.glm.fit))

step(P2.glm.fit, test="LRT")
```

>>>>

```{r}
p2mysummary <- summary(P2)

print(p2mysummary)
```

```{r}
#re-shape of a data frame (for easier saving/showing in manuscript)
P2summary_df <- data.frame(do.call(cbind, lapply(P2, summary)))

print(P2summary_df)
```
```{r}
P2%>%
  filter(Dilution!="NA", Tool!="SD", Tool!="*.CTRL")%>%
  mutate(
    Ct.Cat = ifelse(Ct >=38,"Detected","Positive"),
    Ct.Cat=factor(Ct.Cat))%>%
  group_by(Dilution,Method,Ct.Cat)%>%
  summarise(n=n(),
            mean=mean(Ct))%>%
  arrange(Dilution,mean)
```

@@

```{r Table Best Ct comparing spike and surface recovery}
#Summary of Tool A compared to -1 Serial Dilution Recovery
P1.1Dilution.Summary<-P2%>%
  filter(Dilution=="-1")%>%
  mutate(
    Ct.Cat = ifelse(Ct >=38,"Detected","Positive"),
    Ct.Cat=factor(Ct.Cat))%>%
  group_by(Tool,Method,Ct.Cat)%>%
  summarise(n=n(),
            mean=mean(Ct))%>%
  arrange(mean)%>%
  na.omit(C.Cat)
```
```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","supplement", "P2.-1Dilution.Table.rds")
saveRDS(P1.1Dilution.Summary, file = summarytable_file)
```
A difference of 2 Ct values when compared by methods for each tool type. CDC was better when directly extracted. NTP performed better during a spiked tool and surface recovery procedures. 
Ct loss between Spike and SS recovery are about 3 Ct values, equivalent to a log loss of copies.

@@

```
######################################
#Data fitting/statistical analysis
######################################

### 2021-11-13 code/analysis_code/04-Mods.Rmd
Fixed manuscript and processing scripts
removing unfinished chunks

View proportions of the samples within NTP method
```{r}
P2%>%
  filter(Method=="NTP")%>%
  count(Input)%>%
  mutate(Proportions =n/sum(n))
```
Data Splitting
Split into traiining and testing set
```{r}
# Fix the random numbers by setting the seed 
# This enables the analysis to be reproducible when random numbers are used 
set.seed(123)
# Put 3/4 of the data into the training set; this leaves 1/4 of the data to be used to test 
data_split <- initial_split(P2, prop = 3/4)
## Create data frames for the two sets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```
Create CV object
```{r}
CV_train<- 
  vfold_cv(train_data, v=5, repeats= 5, strata = "Method")
```
Create a recipe
```{r}
fit_rec<-
  recipe(Method~., data = train_data)%>%
  step_dummy(all_nominal())
```
Null Model ? - do i need this?
```{r}
#Ct is a continuous outcome-- need to do RMSE as performance metric

@@

  lm_mod%>%
  fit(Ct~Input*Method, data=P2)%>%
    tidy()

>>>>

View proportions of the samples within NTP method
```{r}
P2%>%
  filter(Method=="NTP")%>%
  count(Input)%>%
  mutate(Proportions =n/sum(n))
```

```{r}
P2%>%
  mutate(Norm.Ct=Ct/Input)
```

Data Splitting
Split into training and testing set
```{r}
# Fix the random numbers by setting the seed 
# This enables the analysis to be reproducible when random numbers are used 
set.seed(123)
# Put 3/4 of the data into the training set; this leaves 1/4 of the data to be used to test 
data_split <- initial_split(P2, prop = 3/4)
## Create data frames for the two sets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```
Create CV object
```{r}
CV_train<- 
  vfold_cv(train_data, v=5, repeats= 5, strata = "Method")
```
Create a recipe
```{r}
fit_rec<-
  recipe(Method~., data = train_data)%>%
  step_dummy(all_nominal())
```
Null Model ? - do i need this?
```{r}
#Ct is a continuous outcome-- need to do RMSE as performance metric

@@

lm_fit<-  lm_mod%>%
  fit(Ct~Input*Method, data=P2)
lm_fit
```
```{r}
new_points<- expand.grid(initial_volume=20,
                         food_regime=)
```

```{r}
  P2%>%
  filter(Dilution!="NA", Tool!="SD", Tool!="*.CTRL")%>%
  mutate(
    Ct.Cat = ifelse(Ct >=38,"Detected","Positive"),
    Ct.Cat=factor(Ct.Cat))%>%
  group_by(Dilution,Method,Ct.Cat)%>%
  summarise(n=n(),
            mean=mean(Ct))%>%
  arrange(Dilution,mean)
```
```{r Table Best Ct comparing spike and surface recovery}
  P2%>%
  filter(Dilution=="-1")%>%
  mutate(
    Ct.Cat = ifelse(Ct >=38,"Detected","Positive"),
    Ct.Cat=factor(Ct.Cat))%>%
  group_by(Tool,Method,Ct.Cat)%>%
  summarise(n=n(),
            mean=mean(Ct))%>%
  arrange(mean)
```

### 2021-11-13 code/processing_code/ProcessingScript.Rmd
Fixed manuscript and processing scripts
removing unfinished chunks

---
title: "Data Processing and Saving"
author: "MYC"
date: "10/29/2021"
output: 
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type:
---
This script loads the 2021-10-23_All.Update.csv, a composite of reports, from `raw-data`.
The script further processes, cleans, splits, and saves the data as rds files in the `processed_data` folder.

@@

Confirm Path to Processed Data and loading of cleaned data
```{r load data}
data_location <- here::here("data","processed_data",".rds")
data<- readRDS(data_location)
glimpse(data)
```

>>>>

---
title: "Data Processing and Saving"
author: "MYC"
date: "10/29/2021"
output: html_document
---
This script loads the 2021-10-23_All.Update.csv, a composite of reports, from `raw-data`.
The script further processes, cleans, splits, and saves the data as rds files in the `processed_data` folder.

@@

### 2021-11-13 products/manuscript/Manuscript.Rmd
Fixed manuscript and processing scripts
removing unfinished chunks

In addition to the comparison of enhancement strategies the effects of the tool used for sampling (macrofoam or knit-fiber), time held, and other environmental variables will be explored any significant effects, with interest in positive impacts to detection.

>>>>

In addition to the comparison of enhancement strategies the effects of the tool used for sampling (macrofoam or knit-fiber), time held, and other environmental variables will be explored any significant effects, with interest in positive impacts to detection [@Jansson2020-cg].
